---
title: "Introduction to jtbdtools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to jtbdtools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 5
)
```

## What is Outcome-Driven Innovation?

Jobs-to-Be-Done (JTBD) theory says customers "hire" products to get a job done. **Outcome-Driven Innovation** (ODI), developed by Tony Ulwick, turns this into a quantitative framework: survey users on how *important* each outcome is and how *satisfied* they are with current solutions, then calculate where the biggest gaps are.

The **opportunity score** formula:

```
opportunity = importance + max(0, importance - satisfaction)
```

When importance exceeds satisfaction, the gap amplifies the opportunity. When satisfaction exceeds importance, opportunity equals importance (the floor). Scores range from 0-20, with anything above 10 considered a high-opportunity outcome.

## Quick Start

```{r setup}
library(jtbdtools)
data(jtbd_sample)
```

The sample dataset contains `r nrow(jtbd_sample)` survey respondents rating 12 objectives across 3 job steps:

```{r}
# See the column structure
names(jtbd_sample)[1:8]
```

### Calculate Scores

```{r}
scores <- get_jtbd_scores(jtbd_sample)
scores[, c("job_step", "objective", "imp.all", "sat.all", "opp.all")]
```

The highest-opportunity objectives have high importance and low satisfaction.

### Compare Segments

```{r}
comparison <- get_jtbd_scores.comparison(jtbd_sample, "segment")
# Show opportunity scores by segment
opp_cols <- grep("^opp\\.", names(comparison), value = TRUE)
comparison[, c("job_step", "objective", opp_cols)]
```

### Opportunity Matrix

```{r opportunity-matrix, fig.cap="Opportunity Score Matrix"}
plot_opportunity_matrix(scores, subtitle = "Sample JTBD Survey (N=200)")
```

## Data Format

Your data must follow this column naming convention:

- `imp__job_step.objective_name` for importance columns
- `sat__job_step.objective_name` for satisfaction columns
- Values should be factors with levels 1-5

Example column names:
- `imp__researching.minimize_time_to_evaluate_options`
- `sat__researching.minimize_time_to_evaluate_options`

See `?jtbd_sample` for a complete example dataset and `vignette("data-preparation")` for SPSS import instructions.
