---
title: "Introduction to JTBDtools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to JTBDtools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)


## Introduction

JTBDtools is an R package designed to facilitate Jobs to be Done (JTBD) analysis. This vignette will guide you through the main functions of the package and demonstrate how to use them effectively.

## Installation

You can install the development version of JTBDtools from GitHub with:

```
{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("charlesrogers/jtbdtools")
```

## Loading the Package

Once installed, you can load the package:

## Usage

```{r setup}
library(jtbdtools)
```


## Main Functions

### get_jtbd_scores()

This function calculates JTBD scores for a single segment.

```{r, eval = FALSE}
scores <- get_jtbd_scores(your_data_frame, "segment_column")
```

### get_jtbd_scores.comparison()

This function simplifies the process of calculating JTBD scores for multiple segments.

```{r, eval = FALSE}
comparison_scores <- get_jtbd_scores.comparison(your_data_frame, "segmentation_column")
```

## Conclusion

JTBDtools provides a comprehensive set of functions for JTBD analysis. By following this guide, you should be able to perform basic analyses and visualizations of your JTBD data.

For more detailed information on each function, please refer to the function documentation by using `?function_name` in the R console.